Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-12-07 prop_letter_ajhs.tex
meeting of dec 7

\begin{suggest}{\andy}{0}
  In this investigation, we explore the implications of extending
  point-like quantum-mechanical probability measures to finite
  intervals. 
\end{suggest}

@@

%% ajh "begin" doubled, replace here; two missing commas
We start our investigation with the concept of $\delta$-determinism, where~$\delta$
quantifies the effect of finite-precision uncertainties on measurement
outcomes. We recast the Kochen-Specker theorem using
$\delta$-determinism to quantify the effects of finite precision and
imperfections on contextuality. When $\delta=0$, the generalized
theorem reduces to the conventional one, but as $\delta$ varies from 0
to 1 we note a transition from contextuality to non-contextuality.
% A principal result is that recasting the Kochen-Specker theorem in 
% terms of ``$\delta$-determinism,'' with~$\delta$ quantifying the 
% effect of finite-precision uncertainties on measurement outcomes, 
% reducing to the purely deterministic Kochen-Specker case for 
% $\delta=0$, can resolve the question of the effect of finite precision 
% and imperfections on contextuality.  
%% ajh kill "In more detail"
\begin{suggest}{\andy}{1}
quantum-mechanical contextuality continues to hold, maintaining the 
Kochen-Specker result, but at a   \emph{certain fixed value} of
$\delta$, there is a sharp transition to   \emph{non-contextuality},
parallel in character to, say, a  phase transition.
These results provide a new insight into the Meyer-Mermin debate by
presenting a theory in which there is a \emph{parameter} interpolating
between what appeared previously to be irreconcilable aspects
of contextuality.
\end{suggest}
The quantum-mechanical requirement for contextuality
continues to hold, thus maintaining the Kochen-Specker result for a
\emph{non-vanishing} range of $\delta$, but that at a \emph{certain
  fixed value} of $\delta$, there is a sharp transition, parallel in
its consequences to, say, a phase transition, to
\emph{non-contextuality}. %% ; that is, suddenly a quantum system can be
%% simulated by a non-contextual hidden variable theory.
%% , turning the
%% system effectively from a quantum system into a classical system. 
% that is, quantum mechanics suddenly fails to hold, and all variables
% can be specified simultaneously, turning the theory effectively into a
% classical theory that can be specified consistently by hidden
% variables.
% \yutsung{The part after ``that is''
%   looks strange.
% \begin{enumerate}
% \item The Kochen-Specker theorem is not about quantum mechanics, is about whether
% quantum mechanics can be simulated by a non-contextual deterministic hidden
% variable theory or not. Hence, ``quantum mechanics suddenly fails to hold''
% doesn't make a lot sense.
% \item The question is whether there exist a QIVPM means ``a classical theory
% consistently by hidden variables.'' At least, a QIVPM is not deterministic, and
% I need to check whether it qualities as a classical probabilistic hidden variable
% theory\ldots(?)
% \end{enumerate}
% }
These results provide a new insight into the Meyer-Mermin debate by
presenting a theory in which there is a \emph{parameter} interpolating
between what appeared previously to be irreconcilable aspects %interpretations
of contextuality.
% ajh- above: I think "interpretations" is not quite right -> "aspects"?

We also investigate the second key aspect of imprecise quantum
measurement, which is its statistical nature as reflected in the
application of the Born rule determining the probability of a given
measurement outcome~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
Here, Gleason's theorem establishes that there is no alternative to
the Born rule by demonstrating, using reasonable continuity arguments
in Hilbert spaces of dimension $d\ge3$, the existence of a unique
state $\rho$ consistent with the statistical predictions computed from
the Born rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
Our question then concerns what happens when infinite precision cannot
be achieved.  We are able to show that, while a QIVPM incorporating
the effects of finite precision might not be consistent with Gleason's
unique state~$\rho$ on all projectors defined on a Hilbert
space~$\Hilb$ of dimension $d\ge3$, there is a mathematically precise
sense in which one recovers the original Gleason theorem
asymptotically.  Specifically, it is possible to construct a class of
QIVPMs representing bounded resources that is parameterized by the
size of the intervals. We then demonstrate that all QIVPMs in this
class are consistent with a non-empty ``ball'' of quantum states whose
radius is defined by the maximal length of the
intervals characterizing the uncertainties. As the size of the intervals  
goes to zero, this ball of quantum states converges to a
point representing the unique state consistent with the Born rule and 
Gleason's theorem. 
\begin{suggest}{\andy}{2}[use PLURAL, ball -> balls, and then, to me, it would
be better as "..converges to a dense set of points."]
We then demonstrate that all QIVPMs in this class are
consistent with non-empty ``balls'' of quantum states whose radii
correspond to the lengths of the intervals characterizing the
uncertainties.  As the sizes of the intervals go to zero, these balls
of quantum states converge to a dense, continuous, set of points
representing the unique states consistent with the Born rule and
Gleason's theorem.
\end{suggest}

%% We furthermore establish a mathematical correlation between the sizes
%% of the intervals and the volume of states that are all consistent with
%% an imprecise measurement.  \andy{``volume of states" are not defined
%%   in the Gleason's section.}

@@

A conventional quantum probability measure can easily be constructed
using the Born rule if one knows the current pure state of the quantum
system.  Specifically, for each pure normalized quantum
state~$\ket{\phi} \in {\cal H}$, the Born rule induces a probability measure
$\muB_{\phi}$ defined as
$\muB_{\phi}(P)=\melem{\phi}{P}{\phi}$. The situation
generalizes to mixed states
$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where $\ket{\phi_j} \in {\cal H}$, $q_j > 0$, and
$\sum_{j=1}^{N}q_{j}=1$, in which case the generalized Born rule
induces a probability measure $\muB_{\rho}$ defined as
$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
\sum_{j=1}^{N}
q_{j}\muB_{\phi_{j}}\left(P\right)$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.

@@

\begin{suggest}{\andy}{5}[To
begin with, "axioms" is COMPLETELY undefined, appears NOWHERE in
the text except here.  So either NAME and LIST (instead of inline
text)  the several statements around Eqs.~(\ref{eq:QIVPM-constraints}) as axioms, or use
another term.  In addition the english "state of the quantum" is
wrong here.  Including fixing that, I would replace the first two
sentences by TEXT \# 5.  It's really strangely written.]
The above construction assumes a mathematical idealization
having known quantum state and infinitely precise measuring
instruments.  In an actual experimental setup with an ensemble of
quantum states that would ideally be identical, but are not actually
identically prepared, with imperfections and inaccuracies in the
measuring devices,  an experimenter might only be able to determine
that the probability of an event $P$ is concentrated in the range
$[0.49,0.51]$ instead of being precisely $0.5$.   The spread in this
range depends on the amount of resources (time, energy, money, etc.)
that are devoted to the experiment.  In the classical setting, this
``fuzziness'' can be formalized by moving to \emph{interval-valued
  probability measures} (IVPMs), which we explore in the next section,
along with our proposed extension to the quantum domain.
\end{suggest}

The above axioms describe a mathematical idealization in which the
%%state of the quantum is known and involving infinitely precise
quantum state is known and involving infinitely precise
measurements. In an actual experimental setup with an ensemble of
quantum states whose states are unknown, that are not exactly
identically prepared, and with small imperfections and inaccuracies in
measuring devices, an experimenter might only be able to determine
that the probability of an event $P$ is concentrated in the range
$[0.49,0.51]$ instead of being precisely $0.5$. The spread in this
range depends on the amount of resources (time, energy, money, etc.)
that are devoted to the experiment. In the classical setting, this
``fuzziness'' can be formalized by moving to \emph{interval-valued
  probability measures} (IVPMs), which we explore in the next section,
along with our proposed extension to the quantum domain.

@@

We will start by reviewing IVPMs in the classical setting and then
propose our quantum generalization. In the classical setting, there
are several proposals for ``imprecise
probabilities''~\citep{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event~$E$ is generalized from
a single \emph{real number} to an \emph{interval}~$[\ell,r]$,
where~$\ell$ intuitively corresponds to the strength of evidence for
the event~$E$ and~$1-r$ corresponds to the strength of evidence
against the same event. Under some additional assumptions, this
interval could be interpreted as the Gaussian width of a probability
distribution. We, however, use general intervals with no constraints
other than the ones needed to maintain coherence: these are described
next.
%% ajh; previous sentence: I am aware of no previous definition of the
%% concept of "the constraints needed to maintain coherence" or what
%% that possibly means in definable sense. I do not know how to fix
%% it, or even if anyone else has trouble with this phrase as I did.

First, for each interval $[\ell,r]$ we have the natural constraint
$0 \leq \ell \leq r \leq 1$ that guarantees that every element of the
interval can be interpreted as a conventional probability. We also
include $\imposs=[0,0]$ and $\necess=[1,1]$ as limiting intervals to
refer to the probability interval for impossible events
and events that are certain. We can write this, respectively, as
$\mu(\emptyset)=\imposs$ and $\mu(\Omega)=\necess$, where $\emptyset$ is
the empty set and $\Omega$ is the event covering the entire
sample space.  For each interval $[\ell,r]$, we also need the dual
interval $[1-r,1-\ell]$ so that if one interval refers to the
probability of an event~$E$, the dual refers to the probability of the
event's complement $\overline{E}$.  For example, if we discover as a
result of an experiment that $\mu(E) = [0.2,0.3]$ for some event~$E$,
we may conclude that $\mu\left(\overline{E}\right) = [0.7,0.8]$ for the
complementary event~$\overline{E}$. In addition to these simple
conditions, there are some subtle conditions on how intervals are
combined, which we discuss next.

@@

\begin{suggest}{\andy}{6}[inverted logic and phrasing.  I would start at "To formalize
this ..." and replace all the way to Eq.~(\ref{eq:hbar})]
We now show that our definition of QIVPMs is consistent
with classical IVPMs in the sense that a restriction of QIVPMs to
mutually commuting events recovers the definition of classical
IVPMs.  However, we must refine this context for the quantum case,
defining a QIVPM  $\bar{\mu}$ to be \emph{consistent} with a state $\rho$ and
projector~$P$ if the interval $\bar{\mu}(P)$ contains the exact
probability calculated by the Born
rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007} , i.e, if:

 To formalize this connection, we first note that in contrast to
the case with conventional quantum probability spaces, there is
generally no unique state~$\rho$ consistent with a QIVPM. We say that
a QIVPM $\bar{\mu}$ is \emph{consistent} with a state $\rho$ and
projector~$P$ if the interval $\bar{\mu}(P)$ contains the exact
probability calculated by the Born rule,
  \begin{equation}
  \muB_{\rho}\left(P\right) = \Tr\left(\rho
  P\right)\in\bar{\mu}\left(P\right)\ .
  \end{equation}
In contrast with conventional probability spaces, there is \emph{no
guarantee} that a unique state $\rho$ consistent with a QIVPM exists.

@@

\begin{definition}[The core of a probability measure] The \emph{core}
$\coreBorn\left(\bar{\mu},\events'\right)$ of a probability measure 
$\bar{\mu}$ relative to a subspace of events $\events'$ is the
collection of all states $\rho$ that are \emph{consistent} with 
$\bar{\mu}$ on every projector in $\events'$, that is
\begin{equation}
\label{eq:hbar}
\coreBorn\left(\bar{\mu},\events'\right) = \set{\rho}{\forall P\in
\events',~\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)} \ .
\end{equation}
\end{definition}
\end{suggest}
%% which coherently introduces the "core" and sets if off as a
%% DEFINITION, etc. 
We now show that our definition of QIVPMs is consistent with classical
IVPMs in the sense that a restriction of QIVPMs to mutually commuting
events recovers the definition of classical IVPMs. To formalize this
connection, we first note that in contrast to the case with
conventional quantum probability spaces, there is generally no unique
state~$\rho$ consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$
is \emph{consistent} with a state $\rho$ and projector~$P$ if the
interval $\bar{\mu}(P)$ contains the exact probability calculated by
the Born rule, i.e, if:
\begin{equation}
\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)
\end{equation}
where $\muB_{\rho}\left(P\right)=\Tr\left(\rho P\right)$
is the probability of the event~$P$ as determined by the Born
rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.

@@

@@

The similar kind of subtleties happens when we want to define the
expectation value of a random variable. Consider an event $E$ such
that $\bar{\mu}(E)=[0.2,0.3]$ and $\bar{\mu}\left(\overline{E}\right)=[0.7,0.8]$.
Given a random variable
\begin{equation}
X\left(\omega\right)=\begin{cases}
1 & \textrm{, if }\omega\in E\textrm{ ;}\\
2 & \textrm{, if }\omega\notin E\textrm{ ,}
\end{cases}
\end{equation}
its expectation value with respect to $\bar{\mu}$ might be naïvely
defined as\begin{subequations}
\begin{eqnarray}
 &  & 1\cdot\bar{\mu}(E)+2\cdot\bar{\mu}\left(\overline{E}\right)\\
 & = & 1\cdot[0.2,0.3]+2\cdot[0.7,0.8]\\
 & = & [1\cdot0.2+2\cdot0.7,1\cdot0.3+2\cdot0.8]\\
 & = & [1.6,1.9]\,.
\end{eqnarray}
\end{subequations}As we discussed in the previous paragraph, the
true probability of $\bar{\mu}(E)$, $\mu(E)$, can be anywhere in
the range $[0.2,0.3]$ and the true probability of $\bar{\mu}\left(\overline{E}\right)$
is $\mu\left(\overline{E}\right)=1-\mu(E)$. If $\mu(E)=0.2$, the expectation
value of $X$ with respect to $\mu$ is 
\begin{equation}
1\cdot\mu(E)+2\cdot\mu\left(\overline{E}\right)=1\cdot0.2+2\cdot0.8=1.8\,;
\end{equation}
if $\mu(E)=0.3$, the expectation value of $X$ with respect to $\mu$
is
\begin{equation}
1\cdot\mu(E)+2\cdot\mu\left(\overline{E}\right)=1\cdot0.3+2\cdot0.7=1.7\,.
\end{equation}
In another word, no matter how we pick $\mu(E)$, the expectation
value of $X$ is in $\left[1.7,1.8\right]$ which is a more realistic
expectation value of $X$ with respect to $\bar{\mu}$. The interval~$\left[1.7,1.8\right]$
is narrower than the naïve expectation value~$[1.6,1.9]$ because
the naïve one combines contradicting situations in the computation.
In general, the computation of the realistic expectation value, called
the Choquet integral, is more complex than what we discussed because
a random variable may have more than two values. Despite its complexity,
it is still a weight average among the values of a random variable
as given in the following definition.

\begin{definition}[Choquet integral~\citep{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}]\label{def:Choquet}Consider
a classical IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[\mul\left(E\right),\mur\left(E\right)\right]$.
We decompose a random variable~$X$ into step functions, but we separate
the positive and negative terms and write like
\begin{equation}
X=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\mathbf{1}_{E_{i}^{s}}\,,
\end{equation}
where $\mathbf{1}_{E_{i}^{s}}$ is the indicator function of $E_{i}^{s}$,
and we order the value of its range from the smallest to the largest
\begin{equation}
x_{N^{-}}^{-}\le\ldots\le x_{1}^{-}\le0\le x_{1}^{+}\le\ldots\le x_{N^{+}}^{+}
\end{equation}
 and $\left\{ E_{i}^{-}\right\} _{i=1}^{N^{-}}$ and $\left\{ E_{i}^{+}\right\} _{i=1}^{N^{+}}$
are all disjoint. Let $E_{i}^{s\prime}=\bigcup_{j\ge i}E_{j}^{s}$
and $\Delta\mu^{*}\left(E_{i}^{s\prime}\right)=\mu^{*}\left(E_{i}^{s\prime}\right)-\mu^{*}\left(E_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
Then, the Choquet integral of $X$ with respect to $\bar{\mu}$ is
\begin{equation}
\int X\rmd\bar{\mu}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\Delta\mul\left(E_{i}^{s\prime}\right),\Delta\mur\left(E_{i}^{s\prime}\right)\right]\,.\label{eq:interval-expectation}
\end{equation}
\end{definition}

Although Def.~\ref{def:Choquet} looks complex, it matches with our
intuition in the previous example. Let
\begin{equation}
\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}\,,\label{eq:core}
\end{equation}
be the set of possible ``true'' probability measure of an IVPM~$\bar{\mu}$.
Then, the following theorem claims the expectation value of $\bar{\mu}$
is the range of the expectation value of the probability measure in
the core of $\bar{\mu}$.

\begin{thm}\label{thm:Rosenmuller}\citep{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}~For
every classical IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ and
any random variable~$X:\Omega\rightarrow\mathbb{R}$, 
\begin{equation}
\int X\rmd\bar{\mu}=\left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu\right]\,.
\end{equation}
\end{thm}

%   To proceed, we use a formulation of the
% ``Mermin-Peres square''~\cite{peres1995quantum,Mermin1990Simple}
% that uses the expectation value of a physical observable with respect
% to a QIVPM, where the interval-valued expectation value is consistent
% with the expectation value of the same observable in conventional
% quantum mechanics with infinite resources. We show that, as long as
% errors and uncertainties remain smaller than a particular value, the
% Kochen-Specker theorem remains valid. In other words, we established a
% rigorous bound for its validity and, therefore, the limits for
% physical reality to remain contextual.

% \begin{thm} Given a Hilbert space $\Hilb$ of dimension~$d\ge3$,
% for every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, and an
% observable~$\mathbf{O}$ with its spectral decomposition~(\ref{eq:spectrum-decomposition}),
% let $\events'$ be the minimal subspace of events containing $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}$,
% then 
% \begin{equation}
% \expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\,.\label{eq:quantum-interval-expectation-core}
% \end{equation}
% \end{thm}

After we defined QIVPMs, we can easily define the expectation value
of an observable with respect to a QIVPM by adopting the idea of the
classical Choquet integral. Notice that the quantum expectation value~(\ref{eq:quantum-expectation})
is the weight average among the eigenvalues with the weight~$\mu(P_{i})$.
Similarly, given a classical random variable~$X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{E_{i}}$,
the expectation value of $X$ with respect to a probability measure~$\mu$
is the weight average among $x_{i}$ with the weight~$\mu(E_{i})$.
Since the definition of Choquet integral is just using a more complex
but reasonable way to compute the weight, we can apply the same algorithm
on an observable and get the following definition.

\begin{definition}Consider a QIVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
for all $P\in\events$. This time, when we express the observable
as its spectral decomposition
\begin{equation}
\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\,,\label{eq:spectrum-decomposition}
\end{equation}
we separate the positive and negative eigenvalues and order its eigenvalues
from the smallest to the largest 
\begin{equation}
\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\,.
\end{equation}
Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
Then, the expectation value of $\mathbf{O}$ with respect to $\bar{\mu}$
is defined as
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\,.\label{eq:quantum-interval-expectation}
\end{equation}
\end{definition}

If we define the multiplication of two singleton
sets~$\left\{ \lambda_{1}\right\} $ and $\left\{ \lambda_{2}\right\} $
to be $\left\{ \lambda_{1}\lambda_{2}\right\} $.

We will now adapt the proof above to show that it is, in general,
impossible to have just the two intervals \imposs\ and \necess: every
QIVPM must be parameterized by a collection of intervals that includes
at least one additional ``fuzzy'' interval and some events must be
associated with such uncertain intervals. The significance of this
observation is that the uncertainty in the intervals is, in contrast
to the classical case, \emph{a fundamental part of quantum
  theory}. There are in fact two sources of uncertainty: one due to
the finite measurement resources and one due to complementarity, which
requires every quantum framework to be truly probabilistic.

???~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA,Griffiths2003}

>>>>

In this investigation, we explore the implications of extending
conventional quantum-mechanical probability measures to include the
effect of imprecise measurements.

@@

%% ajh "begin" doubled, replace here; two missing commas
We start our investigation with the concept of $\delta$-determinism,
where~$\delta$ quantifies the effect of finite-precision uncertainties
on measurement outcomes. We recast the Kochen-Specker theorem using
$\delta$-determinism to quantify the effects of finite precision and
imperfections on contextuality. When $\delta=0$, the generalized
theorem reduces to the conventional one, but as $\delta$ varies from 0
to 1 we note a transition from contextuality to non-contextuality. For
a \emph{non-vanishing} range of $\delta$, quantum-mechanical
contextuality continues to hold, maintaining the Kochen-Specker
result, but at a \emph{certain fixed value}, $\delta = \frac{1}{3}$,
there is a sharp transition to \emph{non-contextuality}, parallel in
character to a phase transition.  These results provide a new insight
into the Meyer-Mermin debate by presenting a theory in which there is
a \emph{parameter} interpolating between what appeared previously to
be irreconcilable aspects of contextuality.

The quantum-mechanical requirement for contextuality
continues to hold, thus maintaining the Kochen-Specker result for a
\emph{non-vanishing} range of $\delta$, but that at a \emph{certain
  fixed value} of $\delta$, there is a sharp transition, parallel in
its consequences to, say, a phase transition, to
\emph{non-contextuality}. %% ; that is, suddenly a quantum system can be
%% simulated by a non-contextual hidden variable theory.
%% , turning the
%% system effectively from a quantum system into a classical system. 
% that is, quantum mechanics suddenly fails to hold, and all variables
% can be specified simultaneously, turning the theory effectively into a
% classical theory that can be specified consistently by hidden
% variables.
% \yutsung{The part after ``that is''
%   looks strange.
% \begin{enumerate}
% \item The Kochen-Specker theorem is not about quantum mechanics, is about whether
% quantum mechanics can be simulated by a non-contextual deterministic hidden
% variable theory or not. Hence, ``quantum mechanics suddenly fails to hold''
% doesn't make a lot sense.
% \item The question is whether there exist a QIVPM means ``a classical theory
% consistently by hidden variables.'' At least, a QIVPM is not deterministic, and
% I need to check whether it qualities as a classical probabilistic hidden variable
% theory\ldots(?)
% \end{enumerate}
% }
These results provide a new insight into the Meyer-Mermin debate by
presenting a theory in which there is a \emph{parameter} interpolating
between what appeared previously to be irreconcilable aspects %interpretations
of contextuality.
% ajh- above: I think "interpretations" is not quite right -> "aspects"?

We also investigate the second key aspect of imprecise quantum
measurement, which is its statistical nature as reflected in the
application of the Born rule determining the probability of a given
measurement outcome~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
Here, Gleason's theorem establishes that there is no alternative to
the Born rule by demonstrating, using reasonable continuity arguments
in Hilbert spaces of dimension $d\ge3$, the existence of a unique
state $\rho$ consistent with the statistical predictions computed from
the Born rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
Our question then concerns what happens when infinite precision cannot
be achieved.  We are able to show that, while a QIVPM incorporating
the effects of finite precision might not be consistent with Gleason's
unique state~$\rho$ on all projectors defined on a Hilbert
space~$\Hilb$ of dimension $d\ge3$, there is a mathematically precise
sense in which one recovers the original Gleason theorem
asymptotically.  Specifically, it is possible to construct a class of
QIVPMs representing bounded resources that is parameterized by the
size of the intervals. We then demonstrate that all QIVPMs in this
class are consistent with a non-empty ``ball'' of quantum states whose
radius is defined by the maximal length of the intervals
characterizing the uncertainties. As the size of the intervals goes to
zero, this ball of quantum states converges to a point representing
the unique state consistent with the Born rule and Gleason's theorem.

@@

A conventional quantum probability measure can easily be constructed
using the Born rule if one knows the current pure normalized quantum
state $\ket{\phi} \in {\cal H}$; then the Born rule induces a
probability measure $\muB_{\phi}$ defined as
$\muB_{\phi}(P)=\melem{\phi}{P}{\phi}$. For mixed states
$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where
$\ket{\phi_j} \in {\cal H}$, $q_j > 0$, and $\sum_{j=1}^{N}q_{j}=1$,
the generalized Born rule induces a probability measure $\muB_{\rho}$
defined as
$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) = \sum_{j=1}^{N}
q_{j}\muB_{\phi_{j}}\left(P\right)$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.

@@

The quantum probability postulates assume a mathematical idealization
in which quantum states and measurements are both infinitely
precise. In an actual experimental setup with an ensemble of quantum
states that would ideally be identical, but are not actually
identically prepared, with imperfections and inaccuracies in measuring
devices, an experimenter might only be able to determine that the
probability of an event $P$ is concentrated in the range $[0.49,0.51]$
instead of being precisely $0.5$. The spread in this range depends on
the amount of resources (time, energy, money, etc.)  that are devoted
to the experiment. In the classical setting, this ``fuzziness'' can be
formalized by moving to \emph{interval-valued probability measures}
(IVPMs), which we explore in the next section, along with our proposed
extension to the quantum domain.

@@

We will start by reviewing IVPMs in the classical setting and then
propose our quantum generalization. In the classical setting, there
are several proposals for ``imprecise
probabilities''~\citep{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event~$E$ is generalized from
a single \emph{real number} to an \emph{interval}~$[\ell,r]$,
where~$\ell$ intuitively corresponds to the strength of evidence for
the event~$E$ and~$1-r$ corresponds to the strength of evidence
against the same event. Under some additional assumptions, this
interval could be interpreted as the Gaussian width of a probability
distribution.

We next introduce probability axioms for IVPMs. First, for each
interval $[\ell,r]$ we have the natural constraint
$0 \leq \ell \leq r \leq 1$ that guarantees that every element of the
interval can be interpreted as a conventional probability. We also
include $\imposs=[0,0]$ and $\necess=[1,1]$ as limiting intervals to
refer to the probability interval for impossible events and events
that are certain. We can write this, respectively, as
$\mu(\emptyset)=\imposs$ and $\mu(\Omega)=\necess$, where $\emptyset$
is the empty set and $\Omega$ is the event covering the entire sample
space.  For each interval $[\ell,r]$, we also need the dual interval
$[1-r,1-\ell]$ so that if one interval refers to the probability of an
event~$E$, the dual refers to the probability of the event's
complement $\overline{E}$.  For example, if we discover as a result of
an experiment that $\mu(E) = [0.2,0.3]$ for some event~$E$, we may
conclude that $\mu\left(\overline{E}\right) = [0.7,0.8]$ for the
complementary event~$\overline{E}$. In addition to these simple
conditions, there are some subtle conditions on how intervals are
combined, which we discuss next.

@@

\newpage

\begin{suggest}{\andy}{6}[inverted logic and phrasing.  I would start at "To formalize
this ..." and replace all the way to Eq.~(\ref{eq:hbar})]
We now show that our definition of QIVPMs is consistent
with classical IVPMs in the sense that a restriction of QIVPMs to
mutually commuting events recovers the definition of classical
IVPMs.  However, we must refine this context for the quantum case,
defining a QIVPM  $\bar{\mu}$ to be \emph{consistent} with a state $\rho$ and
a projector~$P$ if the interval $\bar{\mu}(P)$ contains the exact
probability calculated by the Born
rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}, i.e., 
  \begin{equation}
  \muB_{\rho}\left(P\right) = \Tr\left(\rho
  P\right)\in\bar{\mu}\left(P\right)\ .
  \end{equation}
In contrast with conventional probability spaces, there is \emph{no
guarantee} that a unique state $\rho$ consistent with a QIVPM exists.

@@

\begin{definition}[The core of a probability measure] The \emph{core}
$\coreBorn\left(\bar{\mu},\events'\right)$ of a probability measure 
$\bar{\mu}$ relative to a subspace of events $\events'$ is the
collection of all states $\rho$ that are \emph{consistent} with 
$\bar{\mu}$ on every projector in $\events'$, that is
\begin{equation}
\label{eq:hbar}
\coreBorn\left(\bar{\mu},\events'\right) = \set{\rho}{\forall P\in
\events',~\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)} \ .
\end{equation}
\end{definition}
\end{suggest}
%% which coherently introduces the "core" and sets if off as a
%% DEFINITION, etc.

\newpage

We now show that our definition of QIVPMs is consistent with classical
IVPMs in the sense that a restriction of QIVPMs to mutually commuting
events recovers the definition of classical IVPMs. To formalize this
connection, we first note that in contrast to the case with
conventional quantum probability spaces, there is generally no unique
state~$\rho$ consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$
is \emph{consistent} with a state $\rho$ and projector~$P$ if the
interval $\bar{\mu}(P)$ contains the exact probability calculated by
the Born rule, i.e, if:
\begin{equation}
\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)
\end{equation}
where $\muB_{\rho}\left(P\right)=\Tr\left(\rho P\right)$
is the probability of the event~$P$ as determined by the Born
rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.

@@

\newpage

@@
